\begin{pages}
    \begin{Leftside}
    \selectlanguage{greek}
        \beginnumbering
        \pstart[
        			\chapter*{Κεφάλαιον δ’}
  				\markboth{Fourth chapter}{Fourth chapter}
  				\addcontentsline{toc}{chapter}{Fourth chapter}
				]
		Μετὰ ταῦτα εἶδον, καὶ ἰδού, θύρα ἀνεῳγμένη ἐν τῷ οὐρανῷ, καὶ ἡ φωνὴ ἡ πρώτη ἣν ἤκουσα ὡς σάλπιγγος λαλούσης μετ’ ἐμοῦ λέγουσα· Ἀνάβα ὧδε, καὶ δείξω σοι ἃ δεῖ γενέσθαι μετὰ ταῦτα. καὶ εὐθέως ἐγενόμην ἐν πνεύματι· καὶ ἰδού, θρόνος ἔκειτο ἐν τῷ οὐρανῷ, καὶ ἐπὶ τοῦ θρόνου καθήμενος· ὅμοιος ὁράσει λίθῳ ἰάσπιδι καὶ σαρδίνῳ· καὶ ἶρις κυκλόθεν τοῦ θρόνου ὁμοία ὅρασει σμαραγδίνῳ. καὶ κυκλόθεν τοῦ θρόνου θρόνοι εἴκοσι τέσσαρες· καὶ ἐπὶ τοὺς θρόνους εἶδον τοὺς εἴκοσι καὶ τέσσαρας πρεσβυτέρους καθημένους, περιβεβλημένους ἐν ἱματίοις λευκοῖς, καὶ ἔσχον ἐπὶ τὰς κεφαλὰς αὐτῶν στεφάνους χρυσοῦς. καὶ ἐκ τοῦ θρόνου ἐκπορεύονται ἀστραπαὶ καὶ βρονταὶ καὶ φωναί· καὶ ἑπτὰ λαμπάδες πυρὸς καιόμεναι ἐνώπιον τοῦ θρόνου, ἅ εἰσι τὰ ἑπτὰ πνεύματα τοῦ Θεοῦ· καὶ ἐνώπιον τοῦ θρόνου θάλασσα ὑαλίνη, ὁμοία κρυστάλλῳ. 
		\pend
		\pstart
		καὶ ἐν μέσῳ τοῦ θρόνου καὶ κύκλῳ τοῦ θρόνου τέσσαρα ζῶα γέμοντα ὀφθαλμῶν ἔμπροσθεν καὶ ὄπισθεν. καὶ τὸ ζῶον τὸ πρῶτον ὅμοιον λέοντι, καὶ τὸ δεύτερον ζῶον ὅμοιον μόσχῳ, καὶ τὸ τρίτον ζῷον ἔχον τὸ πρόσωπον ὡς ἄνθρωπος, καὶ τὸ τέταρτον ζῶον ὅμοιον ἀετῷ πετομένῳ. καὶ τὰ τέσσαρα ζῶα, ἓν καθ’ ἐαυτὸ εἴχον ἀνὰ πτέρυγας ἕξ κυκλόθεν, καὶ ἔσωθεν γέμοντα ὀφθαλμῶν, καὶ ἀνάπαυσιν οὐκ ἔχουσιν ἡμέρας καὶ νυκτός, λέγοντα, Ἅγιος, ἅγιος, ἅγιος Κύριος ὁ Θεὸς ὁ παντοκράτωρ, ὁ ἦν καὶ ὁ ὢν καὶ ὁ ἐρχόμενος. 
		\pend
		\pstart
		καὶ ὅταν δώσουσι τὰ ζῶα δόξαν καὶ τιμὴν καὶ εὐχαριστίαν τῷ καθημένῳ ἐπὶ τοῦ θρόνου, τῷ ζῶντι εἰς τοὺς αἰῶνας τῶν αἰώνων, πεσοῦνται οἱ εἴκοσι καὶ τέσσαρες πρεσβύτεροι ἐνώπιον τοῦ καθημένου ἐπὶ τοῦ θρόνου, καὶ προσκυνοῦσι τῷ ζῶντι εἰς τοὺς αἰῶνας τῶν αἰώνων, καὶ βάλλουσι τοὺς στεφάνους αὐτῶν ἐνώπιον τοῦ θρόνου, λέγοντες, Ἄξιος εἶ, Κύριε, λαβεῖν τὴν δόξαν καὶ τὴν τιμὴν καὶ τὴν δύναμιν· ὅτι σὺ ἔκτισας τὰ πάντα, καὶ διὰ τὸ θέλημά σου εἰσὶ καὶ ἐκτίσθησαν.
		\pend
        \endnumbering
    \end{Leftside}
    \begin{Rightside}
        \beginnumbering
        \pstart[
        			\chapter*{Fourth chapter}
				]
		After this I saw — and look! — a door having been opened in Heaven and the first voice I heard — (which spoke) like a trumpet — was speaking to me, saying, “Come up here and I will show you what must happen hereafter. Immediately I was in Spirit, and look! A throne (chair) placed within Heaven and someone was sitting on it; and He who was sitting on it was in appearance like a jasper and carnelian stone and a rainbow was around the throne, which looked as if it was made out of emeralds. And around the throne were (another) twenty-four thrones and upon those thrones were sitting twenty-four elders, (all) clad in white garments and upon their heads were golden crowns. And from the throne (there) came forth (bolts of) lightning, voices and thunder; and (there were) seven flaming torches burning before the throne which were the seven Spirits of God; and (the region) before the throne (was) as the Sea made of glass, like a crystal.
		\pend
		\pstart
		And in the middle of the throne and around the throne (there were) four living creatures, covered with eyes from back to front. And the first creature was like a lion, and the second creature was like a bull and the third creature had the head of a human, and the fourth creature was like a flying eagle. And the four creatures each had six wings (which) were filled with eyes around and within. And without a break — day and night — they were saying, “Holy, holy, holy (is the) Lord God, the Almighty, who was and is and who will come.”
		\pend
		\pstart
		Whenever the creatures give glory, honour and thanks to Him who sits upon the throne — He who will live into the eternity of eternities —, the twenty-four elders fall before the One sitting upon the throne and worship Him who lives into the eternity of eternities. And they throw their crowns before the throne, saying, “You are worthy, our Lord and God, of taking the glory, honour and power, for You created (the) everything; and through Your wish we were and were created.”
		\pend
        \endnumbering
    \end{Rightside}

\end{pages} 
\Pages