\begin{pages}
    \begin{Leftside}
    \selectlanguage{greek}
        \beginnumbering
        \pstart[
        			\chapter*{Κεφάλαιον ε’}
  				\markboth{Fifth chapter}{Fifth chapter}
  				\addcontentsline{toc}{chapter}{Fifth chapter}
				]
		Καὶ εἶδον ἐπὶ τὴν δεξιὰν τοῦ καθημένου ἐπὶ τοῦ θρόνου βιβλίον γεγραμμένον ἔσωθεν καὶ ὄπισθεν, κατεσφραγισμένον σφραγῖσιν ἑπτά. καὶ εἶδον ἄγγελον ἰσχυρὸν κηρύσσοντα φωνῇ μεγάλῃ, Τίς ἐστιν ἄξιός ἀνοῖξαι τὸ βιβλίον, καὶ λῦσαι τὰς σφραγῖδας αὐτοῦ; καὶ οὐδεὶς ἠδύνατο ἐν τῷ οὐρανῷ, οὐδὲ ἐπὶ τῆς γῆς, οὐδὲ ὑποκάτω τῆς γῆς, ἀνοῖξαι τὸ βιβλίον, οὐδὲ βλέπειν αὐτό. καὶ ἐγὼ ἔκλαιον πολλά, ὅτι οὐδεὶς ἄξιος εὑρέθη ἀνοῖξαι καὶ ἀναγνῶναι τὸ βιβλίον, οὔτε βλέπειν αὐτό. 
		\pend
		\pstart
		καὶ εἷς ἐκ τῶν πρεσβυτέρων λέγει μοι, Μὴ κλαῖε· ἰδού, ἐνίκησεν ὁ λέων ὁ ὢν ἐκ τῆς φυλῆς Ἰούδα, ἡ ῥίζα Δαυίδ, ἀνοῖξαι τὸ βιβλίον καὶ λῦσαι τὰς ἑπτὰ σφραγῖδας αὐτοῦ. καὶ εἶδον, καὶ ἰδού, ἐν μέσῳ τοῦ θρόνου καὶ τῶν τεσσάρων ζῴων, καὶ ἐν μέσῳ τῶν πρεσβυτέρων, ἀρνίον ἑστηκὸς ὡς ἐσφαγμένον, ἔχον κέρατα ἑπτὰ καὶ ὀφθαλμοὺς ἑπτά, οἵ εἰσι τὰ ἑπτὰ τοῦ Θεοῦ πνεύματα τὰ ἀπεσταλμένα εἰς πᾶσαν τὴν γῆν. καὶ ἦλθε, καὶ εἴληφε τὸ βιβλίον ἐκ τῆς δεξιᾶς τοῦ καθημένου ἐπὶ τοῦ θρόνου. 
		\pend
		\pstart
		καὶ ὅτε ἔλαβε τὸ βιβλίον, τὰ τέσσαρα ζῶα καὶ οἱ εἰκοσιτέσσαρες πρεσβύτεροι ἔπεσον ἐνώπιον τοῦ ἀρνίου, ἔχοντες ἕκαστος κιθάρας, καὶ φιάλας χρυσᾶς γεμούσας θυμιαμάτων, αἵ εἰσιν αἱ προσευχαὶ τῶν ἁγίων· καὶ ᾄδουσιν ᾠδὴν καινήν, λέγοντες, Ἄξιος εἶ λαβεῖν τὸ βιβλίον, καὶ ἀνοῖξαι τὰς σφραγῖδας αὐτοῦ· ὅτι ἐσφάγης, καὶ ἠγόρασας τῷ Θεῷ ἡμᾶς ἐν τῷ αἵματί σου ἐκ πάσης φυλῆς καὶ γλώσσης καὶ λαοῦ καὶ ἔθνους, καὶ ἐποίησας ἡμὰς τῷ Θεῷ ἡμῶν βασιλεῖς καὶ ἱερεῖς, καὶ βασιλεύσομεν ἐπὶ τῆς γῆς. 
		\pend
		\pstart
		καὶ εἶδον, καὶ ἤκουσα ὡς φωνὴν ἀγγέλων πολλῶν κυκλόθεν τοῦ θρόνου καὶ τῶν ζῴων καὶ τῶν πρεσβυτέρων· καὶ ἦν ὁ ἀριθμὸς αὐτῶν μυριάδες μυριάδων, καὶ χιλιάδες χιλιάδων, λέγοντες φωνῇ μεγάλῃ, Ἄξιόν ἐστι τὸ ἀρνίον τὸ ἐσφαγμένον λαβεῖν τὴν δύναμιν καὶ τὸν πλοῦτον καὶ σοφίαν καὶ ἰσχὺν καὶ τιμὴν καὶ δόξαν καὶ εὐλογίαν. καὶ πᾶν κτίσμα ὅ ἐστιν ἐν τῷ οὐρανῷ καὶ ἐν τῇ γῇ, καὶ ὑποκάτω τῆς γῆς, καὶ ἐπὶ τῆς θαλάσσης ἅ ἐστι, καὶ τὰ ἐν αὐτοῖς πάντα, ἤκουσα λέγοντας, Τῷ καθημένῳ ἐπὶ τοῦ θρόνου καὶ τῷ ἀρνίῳ ἡ εὐλογία καὶ ἡ τιμὴ καὶ ἡ δόξα καὶ τὸ κράτος εἰς τοὺς αἰῶνας τῶν αἰώνων. καὶ τὰ τέσσαρα ζῶα ἔλεγον, Ἀμήν. καὶ οἱ εἰκοσιτέσσαρες πρεσβύτεροι ἔπεσαν καὶ προσεκύνησαν ζῶντι εἰς τοὺς αἰῶνας τῶν αἰώνων.
		\pend
        \endnumbering
    \end{Leftside}
    \begin{Rightside}
        \beginnumbering
        \pstart[
        			\chapter*{Fifth chapter}
				]
		And I saw a (little) book upon the right hand of Him who sits upon the throne — (and things were) written within (it) and on its back (behind it) — (and it was) sealed with seven seals. And I saw a strong angel, announcing (preaching) in a great voice, “Who is worthy of opening the book and removing its seals?” And nobody was able to open the book — nor look at it —, neither in Heaven (the sky), nor upon the Earth, nor below the Earth. And I cried vehemently, as nobody was found worthy of either opening or looking at the book.
		\pend
		\pstart
		And one of the elders says to me saying, “Do not cry. Look, the Lion of the people of Juda — the Root of David — was victorious in opening the book and tearing off its seals. And I saw a Lamb standing as if slain (and) having seven heads and seven eyes — which are the seven Spirits of God, sent into the entire Earth — in the middle of the throne and (in the midst of) the four creatures and among the elders. And it came (forth) and took the book out of the right hand of Him who sits upon the throne.
		\pend
		\pstart
		And once he took the book, the four creatures and the twenty-four elders fell (to their knees) before the Lamb, each having a guitar and golden vials filled with incense which are the prayers of the holy. And they sing a new song, saying “You are worthy of taking the book and opening its seals, since You were slain and purchased for God with Your blood (some people) from every tribe and tongue and people and nation; and You have made them (to be) a kingdom and priests for our God and they shall rule upon the Earth. 
		\pend
		\pstart
		And I saw and I heard the voice(s) of many angels around the throne and the creatures and the elders; and their number was myriads of myriads and thousands of thousands. (And the voice was) saying in a great voice, “The slain Lamb is worthy of taking the power and richness and wisdom and might and honour and glory and blessing.” And every creature (creation, being) which is in Heaven and upon the Earth and below the Earth and upon the sea I heard saying “Blessing(s) and honour and glory and power to Him who sits upon the throne and to the Lamb — into the eternity of eternities.” And the four creatures said, “Amen”, and the elders fell (to their knees) and prayed.
		\pend
        \endnumbering
    \end{Rightside}

\end{pages} 
\Pages